An accelerated algorithm for finding efficient solutions in multiobjective problems with black-box multiextremal criteria\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2022-07-01 2022/OPTIMA/paper.tex
Обедилин рисунки и таблицы

The Pareto front in one of test problems is shown in Fig.~\ref{fig2a} and Fig.~\ref{fig2b}. Here Fig.~\ref{fig2a} corresponds to the Pareto front computed on the uniform grid with the step 0.05 in the search domain whereas Fig.~\ref{fig2b} shows the Pareto front computed by RALR-DA.

@@

The averaged HV indices obtained while solving the two-dimensional bi-criteria problems are presented in Tab.~\ref{tab1} and Fig.~\ref{fig3} where ``Pareto'' corresponds to the estimation obtained by the grid method.

\begin{table}
\caption{Results of the experiment with bi-criteria MCO problems of dimension 2.}
\centering
\begin{tabular}{ccccccc} \hline
 Pareto & RALR-DA & OMOPSO & SMPSO & NSGAII & IBEA & SPEA2 \\ \hline
  6.62 & 6.44 & 5.93 & 5.88 & 5.71 & 5.65 & 5.61 \\ \hline
\end{tabular}
\label{tab1}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig3.pdf} 
\caption{HV indices in bi-criteria 2-dimensional case.}\label{fig3} 
\end{figure}

The second experiment was aimed at solving bi-criteria 4-dimensional MCO problems. 10 test problems have been investigated and for each of them, 100 convolutions (\ref{conv_problem}) with uniformly distributed weight coefficients $\lambda$ were minimized by RALR-DA. 
Tab.~\ref{tab2} contains the results achieved by the methods participated in the experiment and Fig.~\ref{fig4} presents them in graphical form.

\begin{table}
\caption{Results of testing bi-criteria 4-dimensional MCO problems.}
\centering
\begin{tabular}{ccccccc} \hline
 Pareto & RALR-DA & SPEA2 & OMOPSO & IBEA & NSGAII & SMPSO   \\ \hline
  5.04 & 4.71 & 4.53 & 4.45 & 4.39 & 4.39 & 4.37 \\ \hline
\end{tabular}
\label{tab2}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig4.pdf} 
\caption{HV indices in bi-criteria 4-dimensional case.}\label{fig4} 
\end{figure}

The third collection of test problems consisted of 10 two-dimensional MCO benchmarks with 4 criteria. In this experiment RALR-DA in each MCO problem minimized convolutions (\ref{conv_problem}) corresponding to 100 different values of weight coefficients $\lambda$ uniformly distributed in the domain (\ref{lambda}).
Like  the  previous experiments, the results are presented in Tab.~\ref{tab3} and Fig.~\ref{fig5}.

\begin{table}
\caption{Results of testing 2-dimensional MCO problems with 4 criteria.}
\centering
\begin{tabular}{ccccccc} \hline
 Pareto & RALR-DA & OMOPSO & SPEA2 & SMPSO & IBEA & NSGAII   \\ \hline
  23.89 & 23.52 & 22.87 & 22.80 & 22.53 & 20.68 & 19.82 \\ \hline
\end{tabular}
\label{tab3}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig5.pdf} 
\caption{HV indices in 4-criteria 2-dimensional case.}\label{fig5} 
\end{figure}

>>>>

The Pareto front in one of test problems is shown in Fig.~\ref{fig2a} and Fig.~\ref{fig2b}. Here Fig.~\ref{fig2a} corresponds to the Pareto front computed on the uniform grid with the step 0.05 in the search domain whereas Fig.~\ref{fig2b} shows the Pareto front computed by RALR-DA. The averaged HV indices obtained while solving the two-dimensional bi-criteria problems are presented in Tab.~\ref{tab4_6} (series 1) and Fig.~\ref{fig4_6} where ``Pareto'' corresponds to the estimation obtained by the grid method.

@@

The second experiment was aimed at solving bi-criteria 4-dimensional MCO problems. 10 test problems have been investigated and for each of them, 100 convolutions (\ref{conv_problem}) with uniformly distributed weight coefficients $\lambda$ were minimized by RALR-DA. Tab.~\ref{tab4_6} (series 2) contains the results achieved by the methods participated in the experiment and Fig.~\ref{fig4_6} presents them in graphical form.

The third collection of test problems consisted of 10 two-dimensional MCO benchmarks with 4 criteria. In this experiment RALR-DA in each MCO problem minimized convolutions (\ref{conv_problem}) corresponding to 100 different values of weight coefficients $\lambda$ uniformly distributed in the domain (\ref{lambda}).
Like  the  previous experiments, the results are presented in Tab.~\ref{tab4_6} (series 3) and Fig.~\ref{fig4_6}.

\begin{table}
\caption{Results of the experiment with multidimensional MCO problems.}
\centering
\begin{tabular}{cccccccccc} \hline
Series& N& k& Pareto & RALR-DA & OMOPSO & SPEA2 & SMPSO & IBEA & NSGAII   \\ \hline
1& 2&	2 & 6.62 & 6.44 & 5.93 & 5.88 & 5.71 & 5.65 & 5.61 \\ 
2& 4&	2 &  5.04 & 4.71 & 4.53 & 4.45 & 4.39 & 4.39 & 4.37 \\ 
3& 2&	4 &  23.89 & 23.52 & 22.87 & 22.80 & 22.53 & 20.68 & 19.82 \\ \hline
\end{tabular}
\label{tab4_6}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{fig4_6.pdf} 
\caption{Relative backlog of the HV index ($HV_{Pareto} / HV_{alg}$).}\label{fig4_6} 
\end{figure}
